---
title: Investigating Rater Agreement with Skewed Data
author: Geetansh Saxena & Madhavi Sen
output: html_document
params:
  start_date: '2023-11-01'
  end_date: '2024-02-01'
---



Loading necessary libraries
```{r}
library(irr)
library(irrCAC)
library(dplyr)
```


```{r}
source("./utils.R")
```

Create a matrix of binary ratings with missing values
Each row represents an object and each column represents a rater
```{r}
binary_ratings_matrix <- matrix(
  c(
    1, 0, 1, 1,   # Object 1: Rater 1, Rater 2, Rater 3, Rater 4
    0, 1, NA, 0,  # Object 2: Rater 1, Rater 2, Rater 3, NA (missing value)
    1, 1, 1, 1    # Object 3: Rater 1, Rater 2, Rater 3, Rater 4
  ),
  nrow = 3, ncol = 4, byrow = TRUE
)
binary_ratings_matrix
```

Imputing missing values in binary_ratings_matrix
```{r}
imputed_binary_ratings_matrix <- impute_missing_values_matrix(binary_ratings_matrix)
imputed_binary_ratings_matrix
```

```{r}
# Calculate Gwet's AC1
ac1_result <- irrCAC::gwet.ac1.raw(imputed_binary_ratings_matrix)
ac1_result
```

```{r}
# Calculate Krippendorff's Alpha 
alpha_result <- irr::kripp.alpha(imputed_binary_ratings_matrix)
alpha_result
```


## CASE 1: Generating a random binary matrix with 100 subjects, 100 raters, and 20% missing data
```{r}
random_binary_matrix_100x100_missing_20 <- generate_random_binary_matrix(100, 100, 20)
print(random_binary_matrix_100x100_missing_20)
```

Imputing missing values to the random_binary_matrix_100x100_missing_20
```{r}
imputed_random_binary_matrix_100x100_missing_20 <- impute_missing_values_matrix(random_binary_matrix_100x100_missing_20)
print(imputed_random_binary_matrix_100x100_missing_20)

```
Calculating alpha on random_binary_matrix_100x100_missing_20
```{r}
alpha_random_binary_matrix_100x100_missing_20 <- irr::kripp.alpha(random_binary_matrix_100x100_missing_20)
alpha_random_binary_matrix_100x100_missing_20
```


## Calculating Kripps alpha on imputed_random_binary_matrix_100x100_missing_20

```{r}
alpha_imputed_random_binary_matrix_100x100_missing_20 <- irr::kripp.alpha(imputed_random_binary_matrix_100x100_missing_20)
print(alpha_imputed_random_binary_matrix_100x100_missing_20)
```


## Calculating Gwets AC1 on imputed_random_binary_matrix_100x100_missing_20
 
```{r}
ac1_coefficient_imputed_random_binary_matrix_100x100_missing_20 <- irrCAC::gwet.ac1.raw(imputed_random_binary_matrix_100x100_missing_20)

ac1_coefficient_imputed_random_binary_matrix_100x100_missing_20

```


# CASE 2: Generating a random binary matrix with 100 subjects, 100 raters, and 80% missing data

```{r}

random_binary_matrix_100x100_missing_80 <- generate_random_binary_matrix(100, 100, 80)
print(random_binary_matrix_100x100_missing_80)

```




```{r}

imputed_random_binary_matrix_100x100_missing_80 <- impute_missing_values_matrix(random_binary_matrix_100x100_missing_80)
print(imputed_random_binary_matrix_100x100_missing_80)
 
```


## Calculating alpha on random_binary_matrix_100x100_missing_80


```{r}
alpha_random_binary_matrix_100x100_missing_80 <- irr::kripp.alpha(random_binary_matrix_100x100_missing_80)
print(alpha_random_binary_matrix_100x100_missing_80)
```



## Calculating alpha on imputed_random_binary_matrix_100x100_missing_80


```{r}
alpha_imputed_random_binary_matrix_100x100_missing_80 <- irr::kripp.alpha(imputed_random_binary_matrix_100x100_missing_80)
print(alpha_imputed_random_binary_matrix_100x100_missing_80)
```
## Calculating ac1 on imputed_random_binary_matrix_100x100_missing_80
```{r}
ac1_coefficient_imputed_random_binary_matrix_100x100_missing_80 <- irrCAC::gwet.ac1.raw(imputed_random_binary_matrix_100x100_missing_80)

ac1_coefficient_imputed_random_binary_matrix_100x100_missing_80

```
# Comparison of case 1 and case 2

```{r}
simple_comparison <- data.frame(
  Case = c("1", "2"),
  'Missing Data' = c(20, 80),
  Alpha = c(alpha_random_binary_matrix_100x100_missing_20$value, alpha_random_binary_matrix_100x100_missing_80$value),
  AC1 = c(ac1_coefficient_imputed_random_binary_matrix_100x100_missing_20$est$coeff.val,ac1_coefficient_imputed_random_binary_matrix_100x100_missing_80$est$coeff.val) 
)
simple_comparison

```


# Introducing bias


# Simple case to check bias: Generating a random binary matrix with bias for Rater2
# Parameters: 4 subjects, 3 raters, and 20% missing data

```{r}

bias_probabilities <- c(0.1, 0.3, 0.2)  # Adjust bias probabilities for each rater
biased_random_matrix_missing_20 <- generate_random_binary_matrix_with_bias(4, 3, 20, bias_probabilities)
print(biased_random_matrix_missing_20)
```

# Calculate Krippendorff's Alpha for the biased matrix (biased_random_matrix_missing_20)

```{r}

kripp_alpha_biased_random_matrix_missing_20 <- irr::kripp.alpha(biased_random_matrix_missing_20)
kripp_alpha_biased_random_matrix_missing_20
```


# Impute missing values with mean and calculate Gwet's AC1

```{r}

imputed_biased_random_matrix_missing_20 <- impute_missing_values_matrix(biased_random_matrix_missing_20)

gwet_ac1_imputed_biased_random_matrix_missing_20 <- irrCAC::gwet.ac1.raw(imputed_biased_random_matrix_missing_20)

gwet_ac1_imputed_biased_random_matrix_missing_20

```

# The bias_probabilities_range parameter defines the minimum and maximum values for 
# the uniform distribution from which these random bias probabilities are drawn.
```{r}
bias_probabilities_range <- c(0.2, 0.9)  # Adjust the range of bias probabilities
```



# Case 3: Generate a random binary matrix with randomly generated bias for 100 subjects, 100 raters, and 20% missing data
```{r}

randomly_generated_bias__binary_matrix_missing_20 <- generate_random_binary_matrix_with_random_bias(100, 100, 20, bias_probabilities_range)
alpha_randomly_generated_bias__binary_matrix_missing_20 <- irr::kripp.alpha(randomly_generated_bias__binary_matrix_missing_20)
alpha_random_binary_matrix_100x100_missing_20

```




```{r}
imputed_randomly_generated_bias__binary_matrix_missing_20 <- impute_missing_values_matrix(randomly_generated_bias__binary_matrix_missing_20)

ac1_imputed_randomly_generated_bias__binary_matrix_missing_20 <- irrCAC::gwet.ac1.raw(imputed_randomly_generated_bias__binary_matrix_missing_20)

ac1_imputed_randomly_generated_bias__binary_matrix_missing_20

```




```{r}

# Case 4: Generate a random binary matrix with randomly generated bias for 100 subjects, 100 raters and 80% missing data
randomly_generated_bias__binary_matrix_missing_80 <- generate_random_binary_matrix_with_random_bias(100, 100, 80, bias_probabilities_range)

alpha_randomly_generated_bias__binary_matrix_missing_80 <- irr::kripp.alpha(randomly_generated_bias__binary_matrix_missing_80)

alpha_randomly_generated_bias__binary_matrix_missing_80
```




```{r}

imputed_randomly_generated_bias__binary_matrix_missing_80 <- impute_missing_values_matrix(randomly_generated_bias__binary_matrix_missing_80)

ac1_imputed_randomly_generated_bias__binary_matrix_missing_80 <- irrCAC::gwet.ac1.raw(imputed_randomly_generated_bias__binary_matrix_missing_80)

ac1_imputed_randomly_generated_bias__binary_matrix_missing_80
```




```{r}

################################################################################
###################### Comparison of Cases 3 and 4 #############################
################################################################################

bias_comparison <- data.frame(
  Case = c("3", "4"),
  'Missing Data' = c(20, 80),
  Alpha = c(alpha_randomly_generated_bias__binary_matrix_missing_20$value, alpha_randomly_generated_bias__binary_matrix_missing_80$value),
  AC1 = c(ac1_imputed_randomly_generated_bias__binary_matrix_missing_20$est$coeff.val, ac1_imputed_randomly_generated_bias__binary_matrix_missing_80$est$coeff.val) 
)

bias_comparison


```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```



